TCP Congestion Algorithms In Datacenters \\ \vspace{0.3cm} {\large LS Project}

### 2017-12-20 paper/paper.tex
Updated abstract

In datacenters, multiple tenants share a finite amount of bandwidth. When an
uplink is saturated, packets that overflow available buffer space will be
dropped and have to be retransmitted by the sender. When one tenant chooses to
retransmit faster than others, they have an advantage as they will make it
though more quickly. TCP is a connection-oriented protocol which employs
congestion control algorithms which aim to divide the available bandwidth
equally among network users.

Some congestion control algorithms are more aggressive than others, and it has
been reported that some algorithms cause others to back off excessively.
Tenants may, perhaps inadvertedly, cause unfair bandwidth distributions during
times of congestion.

In this research, we compare five popular algorithms under different network
conditions to see how they influence each other. Among those are the newly
developed BBR and DCTCP. We found TODO

>>>>

In datacenters, multiple tenants share a finite amount of bandwidth. When an
uplink is saturated, packets that overflow available buffer space will be
dropped and have to be retransmitted by the sender. When one tenant chooses to
retransmit faster than others, they have an advantage as they will make it
though more quickly. TCP is a connection-oriented protocol which employs
congestion control algorithms. These algorithms aim to divide the available
bandwidth equally between network flows.

Some congestion control algorithms are more aggressive than others, and it has
been reported that some algorithms cause others to back off excessively.
Tenants may, perhaps inadvertedly, cause inequal bandwidth distributions during
times of congestion.

In this research, we compare five algorithms under different network conditions
to assess how they influence each other. We found that only CTCP (Windows)
backs off excessively; all other algorithms behave fairly. The results for CTCP
are anomalous compared to all other algorithms and we conclude that for this
algorithm, future work is needed for a reliable assessment.
